### 2011-01-02 docs/slides/model.tex
Result added
Some slides added.
Batesian and Mullerian mimicry slides.
Additional slides.

\frame
{
	\frametitle{The Model}
}

>>>>

\frame
{
	\begin{center}
		\LARGE The Model: Evolution of Mimicry
	\end{center}
}

\frame
{
	\frametitle{The Model}
	\framesubtitle{Evolution of Mimicry}

	\begin{itemize}
		\item \textbf{Objective:} Build an \textit{agent based} Artificial Life model for simulating the evolution of mimicry.	
		\item Two species of agents:
			\begin{enumerate}
				\item Prey
					\begin{itemize}
						\item Model
						\item Mimic
					\end{itemize}
				\item Predator
			\end{enumerate}
		\item Prey pattern representation: Cellular Automata.
		\item Predator pattern recognition: Hopfield Network.
		\item Environment: Visual representation, 3D, toroidal.
	\end{itemize}	
}

\subsection{Past Work}

\frame
{
	\frametitle{The Model}
	\framesubtitle{Past Work}

	\begin{itemize}
		\item Turner and Huheey:
			\begin{itemize}
				\item \textbf{Focus:} Selective pressure on prey, by learning ability of predator.
				\item Predators use simple Monte Carlo learning or mathematical approach.
			\end{itemize}
		\item Sherratt:
			\begin{itemize}
				\item Co-evolving predator and prey population.
				\item Predators are deterministic, cannot learn from experience.
				\item Predators attack policy is fixed, either attack or avoid.
			\end{itemize}
	\end{itemize}
}

\subsection{FormAL}

\frame
{
	\frametitle{FormAL Framework}
}

\subsection{Prey}

\frame
{
	\frametitle{Prey}
}

\subsection{Predator}

\frame
{
	\frametitle{Predator}
}
